Supporting Non-Functional Requirements in Services Software Development Process: An MDD Approach

### 2013-10-19 SOFSEM2014/FinalVersion/main.tex
All sections reviewed, and modified.

\maketitle
\begin{abstract}
This paper presents an extension to the Service Oriented Development Method (SOD-M) to support the representation of some non-functional requirements. 
Specifically, we propose to extend SOD-M with: 
\textit{(i)} meta-models for representing non-functional requirements in different abstraction levels; 
\textit{(ii)} model-to-model transformation rules, useful to semi-automatically refine Platform Independent Models into Platform Specific Models; and 
\textit{(iii)} rules to transform Platform Specific Models into concrete implementations. 
We apply our proposal to develop a proof-of-concept example.
\end{abstract}

>>>>

\maketitle
\begin{abstract}
This paper presents the $\pi$-SODM method an extension to the Service Oriented Development Method (SOD-M) to support the developement of services software considering their functional and    non-functional requirements. 
Specifically, $\pi$-SODM proposes: 
\textit{(i)} meta-models for representing non-functional requirements in different abstraction levels; 
\textit{(ii)} model-to-model transformation rules, useful to semi-automatically refine Platform Independent Models into Platform Specific Models; and 
\textit{(iii)} rules to transform Platform Specific Models into concrete implementations. 
In order to illustrate the use of this methodology the paper describes how its use to develop a proof-of-concept.
\end{abstract}
